Adopting agile in the large: motivations, success factors and challenges

### 2014-04-14 journal/article.tex
Transformation time and size graphs
Agile methods used

The size of the organizations varied from the minimum included size of 50 to
18,000 people. The median size was 300 people. In 7 studies the size was
presented in terms of teams, ranging from the minimum of 6 teams to 150 teams.
The median was 10 teams. In 8 studies there was no direct indication on size
but the issues discussed revealed that the organization was of large size
accoding to our definition.

Time of transformation

Agile methods used

>>>>

The size of the organizations varied from the minimum included size of 50 to
18,000 people. The median size was 300 people. In 7 studies the size was
presented in terms of teams, ranging from the minimum of 6 teams to 150 teams.
The median was 10 teams. In 8 studies there was no direct indication on size
but the issues discussed revealed that the organization was of large size
accoding to our definition. The distribution of organization sizes is presented
in figure \ref{fig:organization_size}.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/organization_size.pdf}
    \caption{Distribution of organization sizes in primary studies}
    \label{fig:organization_size}
  \end{center}
\end{figure}

Figure \ref{fig:transformation_time} summarizes the publication years of the
primary studies, and the years when the transformations were reported to have
started. All studies and transformations were dated after year 2000. There were
peaks in transformation studies in years 2008 and 2011. The studies were
typically published two years after the start of the transformation.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/transformation_time.pdf}
    \caption{Publication years and reported start years of transformations}
    \label{fig:transformation_time}
  \end{center}
\end{figure}

\subsection{Agile methods used}

\begin{table}
    \begin{tabular}{ l r r r }
        \toprule
        Method    &  Reported in studies   \\
        \midrule
        Scrum            &  28 \\
        XP               &  5  \\
        Scrum with XP    &  6  \\
        Scrum with Lean  &  7  \\
        Other            &  4  \\
        Not specified    &  4  \\
        \bottomrule
    \end{tabular}
    \caption{Agile methods reported in the transformed organization}
    \label{table:agile_methods}
\end{table}

The agile methods reported being used in the transformed organizations are
summarized in table \ref{table:agile_methods}. The most prevalent method was
Scrum, which was the sole agile method mentioned in 28 studies. The second most
mentioned agile method was Extreme Programming (XP). Lean software development
was mentioned in some studies, although combined to Scrum in all cases. Other
agile methods mentioned were Unified Process, ADM, and Rapid Application
Development.

It was quite common that organizations sought to combine agile methods.
Especially Scrum, XP, and Lean software development were used together. In
addition, many cases mentinoed use of XP practices without explicitly stating XP
as the process being used (such as test driven development and continuous
integration). Combining and customizing agile practices was also evident in that
many organizations viewed the agile method as continuously evolving.
Organizations evolved the agile methods for instance through retrospectives and
continuous improvement.
